Ages of Planets and Stars Observed by Kepler

### 2024-04-08 paper/ms.tex
update ms

\subsection{Tally}

@@

%TODO: does JUMP mirror all HIRES data from KOA?
We queried a combination of the Keck Observatory Archive and the
internal CPS archive to collect all HIRES spectra that were available
for the \nplhoststarwgyroagewithgrazingandhighruwe\ stars
with plausible rotation-based ages.
This exercise yielded at least one spectrum for \nlithiumstars\ and 
\nlithiumplanets\ planets.

@@

\startlongtable
\begin{deluxetable}{lllrrrr}
	%\tabletypesize{\footnotesize}
	\tabletypesize{\scriptsize}
	\tablecaption{Young planets and planet candidates.
		%The non-truncated machine readable versions are accessible both
		%through the online journal, and at
		%\url{https://zenodo.org/record/8327508}.
		\label{tab:youngplanets}}
	%\toprule
	%\midrule
	%\endhead
	\startdata
	KOI & Kepler & $t_{\rm gyro}$ & $R_{\rm p}$ & $P_{\rm orb}$ & $f_{\rm RUWE}$ & $f_{\rm grazing}$ \\
	-- &   -- & Myr &    Earths &    days &      bool &   bool  \\
	\hline
	\input{table_subgyr_confirmed} %\\
	%\hline
	\input{table_subgyr_candidate}
	\enddata
	\tablecomments{This table includes X, Y, Z... The machine-readable version,
		available online, includes additional columns for .... 
	}
\end{deluxetable}
%\endlongtable

>>>>

\subsection{Tally}
\label{subsec:tally}

@@

%TODO: does JUMP mirror all HIRES data from KOA?
We queried a combination of the Keck Observatory Archive and the
internal CPS archive to collect all HIRES spectra that were available
for the \nplhoststarwgyroagewithgrazingandhighruwe\ stars
described in Section~\ref{subsec:tally} for which it might be possible
to derive rotation-based ages.

%
We required the spectra to not have the iodine cell in...
%TODO ?!?!?!
%

This exercise yielded at least one spectrum for \nlithiumstars\ and 
\nlithiumplanets\ planets.
These observations were acquired between 6 September 2009 and 18
September 2022.

@@

\startlongtable
\begin{deluxetable}{lllrrrrr}
	%\tabletypesize{\footnotesize}
	\tabletypesize{\scriptsize}
	\tablecaption{Young planets and planet candidates.
		%The non-truncated machine readable versions are accessible both
		%through the online journal, and at
		%\url{https://zenodo.org/record/8327508}.
		\label{tab:youngplanets}}
	%\toprule
	%\midrule
	%\endhead
	\startdata
	KOI & Kepler & $t_{\rm gyro}$ & $R_{\rm p}$ & $P_{\rm orb}$ & $f_{\rm RUWE}$ & $f_{\rm grazing}$ & Spec? \\
  -- &   -- & Myr &    Earths &    days &      bool &   bool  & bool \\
	\hline
	\input{table_subgyr_confirmed} %\\
	%\hline
	\input{table_subgyr_candidate}
	\enddata
	\tablecomments{This table includes X, Y, Z... The machine-readable version,
		available online, includes additional columns for .... 
	}
\end{deluxetable}
%\endlongtable
